\documentclass{resume}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Shivanshu Gupta}
\address{\href{mailto:shivanshukgupta@gmail.com}{shivanshukgupta@gmail.com} \\ \href{https://linkedin.com/in/shivanshukgupta}{Linkedin} \\ \href{https://github.com/ShivanshuKGupta}{Github} \\ \href{https://leetcode.com/u/C0dePhilic}{LeetCode}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
        Languages     & C++, Dart, C, Python, Javascript, Typescript                                             \\
        Technologies  & Flutter, MERN (MongoDB, Express, React, Node.js), Next.js, Firebase, Appwrite, Socket.io \\
        Familiar With & gRPC, Typesense, HTML, CSS, Jaspr, Unity, Kotlin, MySQL, Bash Script, Docker             \\
    \end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    {\bf Indian Institute of Information Technology, Raichur} \hfill {Dec 2021 - 2025} \\
    B. Tech Computer Science and Engineering \hfill {CGPA: 9.1}
\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
    \textbf{Software Developer at \href{https://www.royalcaribbeangroup.com/}{Royal Caribbean Group}} \hfill Mar 2025 - Present\\
    \textit{Technologies: Node.js, React, Next.js, Deno, MongoDB, Redis, Docker, Typesense, WebOS, gRPC}
    \begin{itemize}
        \itemsep -3pt {}
        \item \textbf{Backend as a Service}: Developed a scalable, extensible, secure BaaS to accelerate time-to-market, providing,
              \begin{itemize}
                  \itemsep -3pt {}
                  \item Real-time Database Event Subscriptions
                  \item Extend the backend with Custom Serverless Functions (cron jobs, webhooks, etc.)
                  \item A powerful query engine supporting complex queries, aggregations, and full-/partial-/fuzzy-text search
                  \item A Frontend SDK with API documentation
                  \item Built-in caching and flexible permissions
                  \item Security features such as API keys, sessions, cost-based rate limiting, and more.
              \end{itemize}
        \item \textbf{Next-Gen TV}: Spearheaded the development of a next-generation TV system for \textbf{Royal Caribbean Group}, enabling remote fleet-wide control, real-time analytics, and infrastructure automation.
              \begin{itemize}
                  \itemsep -3pt
                  \item Engineered a remotely manageable TV ecosystem with real-time analytics and automated infrastructure tailored for cruise environments.
                  \item Built an in-house video streaming service, significantly reducing licensing costs—saving millions.
                  \item Navigated limitations of Tizen/WebOS TVs by iteratively migrating the tech stack, optimizing for support, performance, and stability on embedded systems.
                  \item Developed a feature-rich dashboard for remote TV management, issue resolution, logging, and analytics.
                  \item Integrated key functionalities including ship-to-guest messaging, live/multicast video streaming, itinerary management, and connectivity with cruise operations systems.
              \end{itemize}
    \end{itemize}

    \textbf{Contract Developer at \href{https://ngispro.com/}{NGIS Pro}} \hfill Feb 2024 - Feb 2025\\
    \textit{Technologies: Flutter, Node.js, Python, TizenOS, WebOS, Appwrite, Supabase, Docker}
    \begin{itemize}
        \itemsep -3pt {}
        \item \textbf{Televolution}: Led the development of a cruise TV system with remote management, analytics, and automated infrastructure, ensuring ship-to-shore synchronization.
              \begin{itemize}
                  \itemsep -3pt {}
                  \item Developed UIs using \textbf{Flutter}, \textbf{Flutter-Tizen}, \textbf{React}, \textbf{Jaspr}, and finally \textbf{Next.js}, backed by \textbf{Appwrite}; built a \textbf{Node.js} middle server for third-party integrations, and created a dashboard for remote TV control, issue resolution, logging, and analytics.
                  \item Automated infrastructure setup using Bash and Python scripts; implemented ship-to-shore sync logic and replaced HTTP polling with \textbf{WebSockets}, reducing network overhead by \textbf{95\%}.
              \end{itemize}
              % \item Televolution: Led the development of a comprehensive cruise TV system with remote management, analytics, and automated infrastructure, ensuring consistent ship-to-shore synchronization.
              %       \begin{itemize}
              %           \itemsep -3pt {}
              %           \item Developed UIs using \textbf{Flutter}, \textbf{Flutter-Tizen}, \textbf{React}, \textbf{Next.js}, and \textbf{Jaspr}, backed by \textbf{Appwrite}.
              %           \item Built a \textbf{Node.js} middle server for system integration and third-party API/tool support.
              %           \item Created a custom dashboard for remote TV control, issue resolution, logs, and analytics.
              %           \item Automated infrastructure setup/management with Bash and Python scripts.
              %           \item Developed robust data sync system between ship and shore; replaced HTTP polling with \textbf{WebSockets}, reducing network overhead by \textbf{95\%}.
              %       \end{itemize}
        \item \href{https://recruitpick.com}{RecruitPick}: A platform similar to Linkedin, but for the sports community.
              \begin{itemize}
                  \itemsep -3pt {}
                  \item Aimed at addressing talent recruitment challenges by connecting sports companies with potential recruits.
                  \item The app (\href{https://play.google.com/store/apps/details?id=com.recruitpick.app.prod}{Android} \& \href{https://apps.apple.com/in/app/recruit-pick-inc/id6478814537}{iOS}) is currently in BETA and has over 150 users.
              \end{itemize}
    \end{itemize}

    \textbf{SDE Intern at \href{https://stoild.in/}{Stoild Private Limited}} \hfill Dec 2023 - Feb 2024\\
    \textit{Technologies: Flutter, Node.js, Express, MongoDB, WebRTC, Socket.io, Web Scraping}
    \begin{itemize}
        \itemsep -3pt {}
        \item Developed a live streaming and gaming application using \textbf{Flutter}, implementing \textbf{WebRTC} architecture from scratch and managing ICE candidates and SDP with a \textbf{Node.js} signaling server.
        \item Designed and implemented the backend using \textbf{Node.js} and \textbf{MongoDB}.
        \item Implemented web scraping techniques to automate data extraction tasks.
    \end{itemize}

    \textbf{\href{https://drive.google.com/file/d/16NqRxg5LFhZu0WkdqG3z83XnLyf5P2UO/view?usp=sharing}{Flutter Intern at IIIT Raichur}} (\href{https://github.com/ShivanshuKGupta/hustle_stay}{Github}) \hfill June - Aug 2023\\
    \textit{Technologies: Flutter, Firebase}
    \begin{itemize}
        \itemsep -3pt {}
        \item Developed an application for seamless attendance management, complaint reporting with updates, and chat functionality. Streamlined requests for vehicles, mess, and other services using Flutter and Firebase.
        \item Aimed to digitalize all paperwork related to hostel management.
    \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% OPEN SOURCE CONTRIBUTIONS
%----------------------------------------------------------------------------------------

\begin{rSection}{Open Source Contribution}
    \textbf{\href{https://docs.gazelle-dart.dev/}{Gazelle - Dart Backend Framework}}: Contributed to the CLI by implementing hot-reload using Dart VM, resolving cross-platform issues, fixing bugs, and adding features to enhance usability. \hfill \href{https://github.com/intales/gazelle/commits?author=ShivanshuKGupta}{PR}
    % \begin{itemize}
    % \item Enhanced the CLI by adding hot-reload functionality using Dart's VM.
    % \item Addressed cross-platform compatibility issues with the cli.
    % \item Fixed numerous bugs and introduced additional CLI features to improve overall usability.
    % \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
    \textbf{Remote App (\href{https://github.com/ShivanshuKGupta/remote}{Github})} \textit{Technologies: Flutter, Python, UDP Sockets}\hfill May 2023
    \begin{itemize}
        \itemsep -3pt {}
        \item A smartphone app to fully control your PC on the same network remotely.
        \item Seamlessly control PC's keyboard and mouse from mobile.
        \item Real-time feedback via screenshots.
    \end{itemize}

    \textbf{Judge (\href{https://github.com/ShivanshuKGupta/Judge}{Github})} \textit{Technologies: Python}\hfill Apr 2023
    \begin{itemize}
        \itemsep -3pt {}
        \item Coding Assignment Checker with a plagiarism detector.
        \item Uses dolos as its plagiarism checker.
        \item Supports C, C++ and Python, but can easily be extended for other programming languages.

    \end{itemize}

    \textbf{Steps Recorder (\href{https://github.com/ShivanshuKGupta/Steps-Recorder}{Github})} \textit{Technologies: Flutter, Python} \hfill Oct 2023
    \begin{itemize}
        \itemsep -3pt {}
        \item Designed and developed a desktop app to record user actions as scripts, enabling users to edit and replay them, streamlining repetitive and meticulous tasks.
    \end{itemize}

    % \textbf{Feedback Hub (Academic Project) (\href{https://github.com/ShivanshuKGupta/feedback_hub}{Github})} \textit{Technologies: Flutter, Strapi}\hfill Nov 2023
    % \begin{itemize}
    %     \itemsep -3pt {}
    %     \item Streamlined feedback management among students, teachers, and parents, featuring dedicated panels for courses and mark sheets, and allowing students and parents to provide feedback to teachers and vice versa, enhancing transparency within the educational ecosystem.
    % \end{itemize}

    \textbf{snIIITcheR (Academic Project)} \textit{Technologies: Unity, Photon Engine} \hfill May 2022
    \begin{itemize}
        \itemsep -3pt {}
        \item An online multiplayer game inspired by the well-known game “Among Us” made with \textbf{Unity} \& \textbf{Photon Engine}.
    \end{itemize}

    \textbf{\href{https://pub.dev/packages/trans_flutter}{Trans\_Flutter}}
    \begin{itemize}
        \itemsep -3pt {}
        % \item A powerful \textbf{\href{https://pub.dev/packages/fluttertrans}{CLI}}-driven package that automates the translation of all strings in your Flutter codebase at compile time, enabling seamless internationalization with minimal effort.
        \item A \textbf{\href{https://pub.dev/packages/fluttertrans}{CLI}} driven tool that scans your Flutter codebase, translates all strings into multiple languages at compile time, and automates internationalization with minimal setup.
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% Packages
%----------------------------------------------------------------------------------------
% \begin{rSection}{Dart/Flutter Packages}
%     \begin{itemize}
%         \itemsep -3pt {}
% \item \textbf{\href{https://pub.dev/packages/trans_flutter}{Trans\_Flutter}}: A powerful \textbf{\href{https://pub.dev/packages/fluttertrans}{CLI}}-driven package that automates the translation of all strings in your Flutter codebase at compile time, enabling seamless internationalization with minimal effort.
%     \end{itemize}
% \end{rSection}

%----------------------------------------------------------------------------------------
% AWARDS AND ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Achievements}

    \begin{itemize}
        \itemsep -3pt {}
        \item Secured \href{https://drive.google.com/file/d/1BdOPAlKCXyNEZf-ujJ5Iu8lBBra77hJg/view?usp=sharing}{Rank 1} among all first-year students and 5th place institute-wide in the CodeRush Coding Challenge at IIIT Raichur.
              % \item Secured an \href{https://drive.google.com/file/d/1b_JE3MbNI2eW9xpYvC1NWCfUGChuEVBy/view?usp=sharing}{international rank of 55} across 70 countries, 70,000 schools and 1,400+ cities, and millions of participants in National Cyber Olympiad 2018 (SOF).
              % \item And again in 2019 secured an \href{https://drive.google.com/file/d/1bnRRCB6FZKDpJm0-Ogz15o56iG2QN_1t/view?usp=sharing}{international rank of 100} in the same competition.
    \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% POSITIONS OF RESPONSIBILITY
%----------------------------------------------------------------------------------------

\begin{rSection}{Positions of Responsibility - IIIT Raichur}
    \begin{itemize}
        \itemsep -3pt {}
        \item \textbf{SciTech Secretary} \hfill March 2023 - Nov 2023
        \item \textbf{CodeSoc Coordinator} \hfill Oct 2022 - March 2023
        \item \textbf{Google Developer Student Club Lead} \hfill Aug 2022 - Aug 2023
        \item \textbf{Competitive Programming Lead - Google DSC} \hfill Aug 2022 - Aug 2023
        \item \textbf{Teaching Assistant} \hfill Mar 2023 - Dec 2023
    \end{itemize}
\end{rSection}

\end{document}