\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Shivanshu Gupta} % Your name
% You can merge both of these into a single line, if you do not have a website.
% \address{(+91) 74408 24858 \\ shivanshu-gupta.web.app} 
\address{(+91) 74408 24858 \\ \href{mailto:shivanshukgupta@gmail.com}{shivanshukgupta@gmail.com} \\ \href{https://linkedin.com/in/shivanshukgupta}{Linkedin} \\ \href{https://github.com/ShivanshuKGupta}{Github}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

% \begin{rSection}{OBJECTIVE}

% Eager learner seeking diverse and innovative tech skills and techniques.

% \end{rSection}
%----------------------------------------------------------------------------------------
% SKILLS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

   \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Languages & C++, Dart, C, Python, Javascript, Typescript                                  \\
      Technologies          & Flutter, Node.js, Express, MongoDB, Firebase, Appwrite, Supabase, Docker, Git \\
      Familiar With         & HTML, CSS, Jaspr, Unity, Kotlin, MySQL, Strapi, Bash Script                   \\
   \end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

   {\bf Indian Institute of Information Technology, Raichur} \hfill {Dec 2021 - Present} \\
   B. Tech | Computer Science and Engineering \hfill {Current GPA: 9.1}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{EXPERIENCE}

   \textbf{Contract Developer at \href{https://ngispro.com}{NGIS Pro}} \hfill Feb - Dec 2024\\
   \textit{Technologies: Flutter, Node.js, Python, TizenOS, WebOS, Appwrite, Supabase, Docker, Jaspr}
   \begin{itemize}
      \itemsep -3pt {}
      \item Televolution: Led the design and development of an internal TV-based solution, replacing HTTP polling with
            WebSockets to implement push-based updates to achieve a \textbf{95\% reduction in network traffic}. Also managed
            synchronization and integration systems to deliver a user-friendly and efficient product.
      \item \href{https://recruitpick.com}{RecruitPick}: Developed a platform for the sports community to address talent recruitment challenges by connecting sports companies with potential recruits. The app (\href{https://play.google.com/store/apps/details?id=com.recruitpick.app.prod}{Android} \& \href{https://apps.apple.com/in/app/recruit-pick-inc/id6478814537}{iOS}) is currently in BETA and has over 150 users.
   \end{itemize}

   \textbf{SDE Intern at \href{https://stoild.in/}{Stoild Private Limited}} \hfill Dec 2023 - Feb 2024\\
   \textit{Technologies: Flutter, Node.js, Express, MongoDB, WebRTC, Socket.io, Web Scraping}
   \begin{itemize}
      \itemsep -3pt {}
      \item Built a live streaming and gaming app in Flutter, implementing WebRTC architecture from scratch with Node.js signaling (ICE candidates, SDP).
      \item Developed backend services using Node.js and MongoDB, and automated data extraction through web scraping.
   \end{itemize}

   \textbf{\href{https://drive.google.com/file/d/16NqRxg5LFhZu0WkdqG3z83XnLyf5P2UO/view?usp=sharing}{Flutter Intern at IIIT Raichur}} (\href{https://github.com/ShivanshuKGupta/hustle_stay}{Github}) \hfill June - Aug 2023\\
   \textit{Technologies: Flutter, Firebase}
   \begin{itemize}
      \itemsep -3pt {}
      \item Developed a \textbf{hostel management app} using \textbf{Flutter} and \textbf{Firebase}, digitalizing attendance, complaint tracking, service requests, and chat functionality.
   \end{itemize}
\end{rSection}

\begin{rSection}{Open Source Contribution}
   \begin{itemize}
      \item     \textbf{\href{https://docs.gazelle-dart.dev/}{Gazelle}}: Enhanced the CLI with hot-reload functionality, ensured cross-platform compatibility, fixed bugs, and added features to improve usability.
   \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
   \begin{itemize}
      % \item \textbf{TV App}: Designed and developed a TV-based solution for \textbf{LG} (WebOS) and \textbf{Samsung} (Tizen OS), implementing real-time updates, synchronization and integration systems to deliver a user-friendly and efficient product. | \textit{Node js, Tizen OS, Web OS, Flutter, Flutter-Tizen, Docker, Jaspr, Python}
      \item \textbf{\href{https://github.com/ShivanshuKGupta/remote}{Remote}}: A smartphone app to control your PC on the same network remotely. \hfill \textit{Flutter, Python}
      \item \textbf{\href{https://pub.dev/packages/fluttertrans}{Flutter\_Trans}}: A Flutter solution for automating app internationalization (i18n). \hfill \textit{Dart}
      \item \textbf{\href{https://github.com/ShivanshuKGupta/Judge}{Judge}}: Coding Assignment Checker with an inbuilt plagiarism detector. \hfill \textit{C++, Python}
      \item \textbf{\href{https://github.com/ShivanshuKGupta/Steps-Recorder}{Steps Recorder}}: Designed and developed a desktop app to record user actions as scripts, enabling users to edit and replay them, streamlining repetitive and meticulous tasks. \hfill \textit{Flutter, Python, Dart}
   \end{itemize}
\end{rSection}
%----------------------------------------------------------------------------------------
% AWARDS AND ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Achievements}

   \begin{itemize}
      \itemsep -3pt {}
      \item \textbf{CodeRush Coding Challenge IIIT Raichur}: \href{https://drive.google.com/file/d/1BdOPAlKCXyNEZf-ujJ5Iu8lBBra77hJg/view?usp=sharing}{Rank 1 Junior}
      \item \textbf{SOF NCO}: \href{https://drive.google.com/file/d/1b_JE3MbNI2eW9xpYvC1NWCfUGChuEVBy/view?usp=sharing}{55th International Rank(2018)} | \href{https://drive.google.com/file/d/1bnRRCB6FZKDpJm0-Ogz15o56iG2QN_1t/view?usp=sharing}{100th International Rank(2019)}
   \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% POSITIONS OF RESPONSIBILITY
%----------------------------------------------------------------------------------------

% \begin{rSection}{Positions of Responsibility}

% \textbf{SciTech Secretary - IIIT Raichur} \hfill March 2023 - Nov 2023
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Organized technical events and managed club activities, fostering innovation and engagement.
%  \end{itemize}

% \textbf{CodeSoc Coordinator - IIIT Raichur} \hfill Oct 2022 - March 2023
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Led activities for the coding club, enhancing technical skills and community engagement.
%  \end{itemize}

% \textbf{Competitive Programming Lead - Google DSC IIIT Raichur} \hfill Aug 2022 - Aug 2023
%  \begin{itemize}
%     \itemsep -3pt {} 
%      \item Promoted competitive programming and facilitated coding competitions.
%  \end{itemize}

% \textbf{Teaching Assistant}
%  \begin{itemize}
%     \itemsep -3pt {}
%      \item Introduction to Data Structures \hfill Mar 2023 - June 2023
%      \item Design and Analysis of Algorithms \hfill Aug 2023 - Nov 2023
%      \item Introduction to Programming \hfill Aug 2023 - Dec 2023
%  \end{itemize}
% \end{rSection}

%----------------------------------------------------------------------------------------
% END LINE
%----------------------------------------------------------------------------------------
% \begin{center}
%     \rule{0.5\linewidth}{0.5pt} \\ % A horizontal line
%     \small \textit{End of Document} \\ % A small italicized text
%     \vspace{0.5cm}
%     % \includegrahics[width=1.5cm]{example-logo.png} % Optional logo or image if applicable
% \end{center}
\end{document}